ms_figures

### 2018-01-23 man/ms_figures.Rmd
update figures and tables

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=3, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1))) +
  scale_color_manual(values=c(col2005, col2012, colref))

@@

Figure 2. Profile of montly EVI values for *Q. pyrenaica* forests during the 2005 (*green*) and 2012 (*blue*) drought events and for the reference period (*gray*) (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b).

Comparison of EVI profile for the reference period (*grey*) and the 2005 (*green*) and 2012 (*blue*) drought events

### Figure R2 = 3 
```{r}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)

# NO plot rrs 
mhuber_filter <- mhuber %>% filter(var != 'rrs')

pd <- position_dodge(.2)

robust_plot_evi_drought <-
  ggplot(mhuber_filter, 
         aes(x = as.factor(disturb_year), y = M.Huber, 
             color = site, 
             group = site, 
             fill = site)) +
  geom_errorbar(
    aes(ymin = lower.ci, ymax = upper.ci),
    width = .1, size = 0.7, position = pd) +
  geom_line(aes(group = site, color = site, linetype = site), position = pd) +
  geom_point(shape = 21, size = 2.5, position = pd) +
  geom_text_repel(aes(label=Letter), 
                  nudge_x = 0.3, size = 5,
                  segment.size = 0) +
  facet_wrap(
    ~var_sorted, nrow = 1, scales = "free_y",
    labeller = as_labeller(c(
      "0_rt" = "Resistance",
      "1_rc" = "Recovery",
      "2_rs" = "Resilience"))) +
  scale_color_manual(values = c("black", "blue")) +
  scale_fill_manual(values = c("black", "blue")) + theme_bw() +
  scale_linetype_manual(values = c("solid", "dashed")) +
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    legend.position = "bottom") +
  ylab("") + xlab("Drought event")

robust_plot_evi_drought 
```

>>>>

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=1.5, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1))) +
  scale_color_manual(values=c(col2005, col2012, colref))

@@

Figure 2. Comparison of EVI profile for the reference period (*gray*) and during the 2005 (*green*) and 2012 (*blue*) drought events (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b). Error bars show standard error.

### Figure 3

```{r}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)
mhuberbai <- read.csv(here("/out/anovas_resilience/huber_bai", "robust_mhuber.csv"), header = TRUE)

# NO plot rrs 
mhuber_filter <- mhuber %>% filter(var != 'rrs') %>% mutate(disturb_year = as.factor(disturb_year))
mhuberbai_filter <- mhuberbai %>% filter(var != 'rrs') %>% mutate(disturb_year = as.factor(disturb_year))

pd <- position_dodge(.2)
line_lwd <- .8

aes_disturb <- aes(x = disturb_year, y = M.Huber, 
                   color = site, group = site, 
                   fill = site, linetype=site,
                   shape = site, 
                   ymin = lower.ci, ymax = upper.ci)
aes_site <- aes(x = site, y = M.Huber, 
                color = disturb_year, group=disturb_year, 
                fill=disturb_year, linetype=disturb_year,
                shape = disturb_year, 
                ymin = lower.ci, ymax = upper.ci)

theme_res <- list(
  geom_errorbar(width=.2, position=pd, lwd=line_lwd), 
  geom_line(position = pd, lwd=line_lwd),
  geom_point(size = 2.5, position = pd), 
  facet_wrap(
    ~var_sorted, nrow = 1, scales="free_y",
    labeller = as_labeller(c(
      "0_rt" = "Resistance",
      "1_rc" = "Recovery",
      "2_rs" = "Resilience"))),
  geom_text_repel(aes(label=Letter), 
                  nudge_x = - 0.5,
                  nudge_y = 0.01,
                  direction="both", 
                  size = 3.5, show.legend = FALSE,
                  segment.size = 0.5, 
                  segment.alpha = 0.5),
  theme_bw(), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),  
  ylab("Response value"), 
  xlab("")
)

theme_evi <-  list(
  scale_color_manual(values = c("black", "blue")),
  scale_shape_manual(values=c(19, 22)),
  scale_fill_manual(values = c("black", "blue")),
  scale_linetype_manual(values = c("solid", "solid"))
)

theme_bai <- list(
  scale_color_manual(values=c('black','blue','blue')), 
  scale_shape_manual(values=c(19, 22, 15)),
  scale_fill_manual(values=c('black','white','blue')),  
  scale_linetype_manual(values=c("solid", "solid", 'solid'))
)
```

```{r}
# EVI_drought 
res_evi_drought <-
  ggplot(mhuber_filter, aes_disturb) + 
  theme_res + theme_evi + theme(legend.position='top') + 
  ggtitle("a) EVI")

# BAI_drought 
res_bai_drought <-
  ggplot(mhuberbai_filter, aes_disturb) + 
  theme_res + theme_bai + theme(legend.position='bottom') + 
  xlab('Drought event') + 
  ggtitle("b) BAI")

```

```{r, fig.height=7}
res_evi_drought  + res_bai_drought + plot_layout(ncol=1)
```

Figure 3. Response of northern (*black*) and southern (*blue*) populations of *Q. pyrenaica* forests to drought in terms of resistance, recovery and resilience of greenness (EVI; a) and tree growth (BAI; b) for the years 2005 and 2012. Different letters above bars indicate significant post hoc differences between groups (see material and methods).

### Figure 4
```{r}
theme_de <- list(
  scale_color_manual(values=c('black','red')), 
  scale_shape_manual(values=c(19, 15)),
  scale_fill_manual(values=c('black','red')),  
  scale_linetype_manual(values=c("solid", "solid")),
  labs(color = 'Drougth event', fill='Drougth event', linetype='Drougth event', shape='Drougth event')

)

# EVI_site
res_evi_site <-
  ggplot(mhuber_filter, aes_site) + 
  theme_res + theme_de + theme(legend.position='top') + 
  ggtitle("a) EVI")

# BAI_site
res_bai_site <-
  ggplot(mhuberbai_filter, aes_site) + 
  theme_res + theme_de + theme(legend.position='bottom') + 
  xlab('Site') + 
  ggtitle("b) BAI") 
```

```{r}
res_evi_site  + res_bai_site + plot_layout(ncol=1)
```

Figure 4. Response of *Q. pyrenaica* forests to 2005 (*black*) and 2012 (*red*) drought events in terms of resistance, recovery and resilience of greenness (EVI; a) and tree growth (BAI; b) by site. Different letters above bars indicate significant post hoc differences between groups (see material and methods).
